Ensembler: Enabling high-throughput molecular simulations at the superfamily scale

### 2015-03-22 manuscript/ms.tex
Revised Fig 1 caption.

  \caption{{\bf Diagrammatic representation of the various stages of the Ensembler pipeline.}
  The number of viable models surviving each stage of the pipeline are shown, either for all tyrosine kinases (\emph{All TKs}) or representative individual kinases (\emph{SRC} and \emph{ABL}).
  In addition, the typical timing on a cluster (containing Intel Xeon E5-2665 2.4GHz hyperthreaded processors and NVIDIA GTX-680 or GTX-Titan GPUs) is reported to exemplify the resources required per model and for modeling the entire set of tyrosine kinases.
  Note that \emph{CPU-h} denotes the number of hours consumed by the equivalent of a single hyperthread and \emph{GPU-h} on a single GPU---parallel execution can reduce wall clock time nearly linearly.
  }
  \label{figpipeline}
\end{figure*}

@@

Selection of templates from the PDB simply requires passing a list of PDB IDs as a comma-separated string, e.g.~{\tt -{}-query 2H8H,1Y57}.
Specific PDB chain IDs can optionally also be selected via the {\tt -{}-chainids} flag.
The program retrieves structures from the PDB server, as well as associated data from the SIFTS service (\href{http://www.ebi.ac.uk/pdbe/docs/sifts/}{www.ebi.ac.uk/pdbe/docs/sifts}) (CITE: Velankar Nucleic Acids Res 2013), which provides residue-level mappings between PDB and UniProt entries.
The SIFTS data is used to extract template sequences, retaining only residues which are resolved and match the equivalent residue in the UniProt sequence---non-wildtype residues are thus removed from the template structures.
Furthermore, PDB chains with less than a given percentage of resolved residues (default: 70\%) are filtered out.
Sequences are stored in a FASTA file, with identifiers of the form {\tt [UniProt mnemonic]\_D[UniProt domain index]\_[PDB ID]\_[PDB chain ID]}, e.g. {\tt SRC\_HUMAN\_D0\_2H8H\_A}.
Matching residues then extracted from the original coordinate files and stored as PDB-format coordinate files.

>>>>

  \caption{{\bf Diagrammatic representation of the various stages of the Ensembler pipeline and illustrative statistics for modeling all human tyrosine kinase catalytic domains.}
  On the left, the various stages of the {\bf Ensembler} pipeline are shown.
  On the right, the number of viable models surviving each stage of the pipeline is shown for modeling all 90 tyrosine kinases (\emph{All TKs}) and representative individual tyrosine kinases (\emph{SRC} and \emph{ABL}).
  Typical timings on a computer cluster (containing Intel Xeon E5-2665 2.4GHz hyperthreaded processors and NVIDIA GTX-680 or GTX-Titan GPUs) is reported to illustrate resource requirements per model for modeling the entire set of tyrosine kinases.
  Note that \emph{CPU-h} denotes the number of hours consumed by the equivalent of a single CPU hyperthread and \emph{GPU-h} on a single GPU---parallel execution via MPI reduces wall clock time nearly linearly.
  }
  \label{figpipeline}
\end{figure*}

@@

Selection of templates from the PDB simply requires passing a list of PDB IDs as a comma-separated string, e.g.~{\tt -{}-query 2H8H,1Y57}.
Specific PDB chain IDs can optionally also be selected via the {\tt -{}-chainids} flag.
The program retrieves structures from the PDB server, as well as associated data from the SIFTS service (\href{http://www.ebi.ac.uk/pdbe/docs/sifts/}{www.ebi.ac.uk/pdbe/docs/sifts}) {\color{red}(CITE: Velankar Nucleic Acids Res 2013)}, which provides residue-level mappings between PDB and UniProt entries.
The SIFTS data is used to extract template sequences, retaining only residues which are resolved and match the equivalent residue in the UniProt sequence---non-wildtype residues are thus removed from the template structures.
Furthermore, PDB chains with less than a given percentage of resolved residues (default: 70\%) are filtered out.
Sequences are stored in a FASTA file, with identifiers of the form {\tt [UniProt mnemonic]\_D[UniProt domain index]\_[PDB ID]\_[PDB chain ID]}, e.g. {\tt SRC\_HUMAN\_D0\_2H8H\_A}.
Matching residues then extracted from the original coordinate files and stored as PDB-format coordinate files.
